---
title: "Plain Models"
output:
  html_document:
    df_print: paged
---


## Libraries
```{r Libraries, message=FALSE, warning=FALSE}
library(dplyr) 
library(psych)
library(readxl)
library(writexl)
library(kableExtra)

# Econometrics
library(tidyverse)
library(plm)
library(sandwich)
library(lmtest)
library(xtable)
library(stargazer)
```

## Downloading the data
```{r Data dowloading}
# Downloading
wide_data <- read_csv('C:/Users/Kolya/Documents/New_studies/Diploma/Data/Data_use/Wide_united_data.csv',
                      show_col_types = FALSE)

long_data <- read_csv('C:/Users/Kolya/Documents/New_studies/Diploma/Data/Data_use/Long_united_data.csv',
                      show_col_types = FALSE)


# Exporting them back to fix QGIS coding issues
write_xlsx(wide_data,
           'C:/Users/Kolya/Documents/New_studies/Diploma/Data/Data_use/Wide_united_data_geo.xlsx')
write_xlsx(long_data,
           'C:/Users/Kolya/Documents/New_studies/Diploma/Data/Data_use/Long_united_data_geo.xlsx')
# Observing the tables
wide_data

long_data
```
## Descriptive statistics
```{r Descriptive statistics, message=FALSE, warning=FALSE}
# For all the variables
Desc_stat <- long_data %>% psych::describe()

# For diversification indexes
Index_stat <- Desc_stat[c(4:6), c(2, 3:4, (8:9))]


# row.names(Index_stat) <- c('Theil index', 'Extensive Margin', 'Intensive Margin')
xtable(Index_stat, caption = 'Descriptive statistics', digits = 3, type = "latex")
```
## Correlation matrix
```{r Correlation matrix}

res1 <- cor(long_data[, c(3:length(long_data))])
res1

library(ggcorrplot)

#visualize correlation matrix
ggcorrplot(cor(long_data[, c(3:length(long_data))]))
```
Import and IM are strongly correlated - 0.98. Might be a problem.


## Create a dataset for 2018
2018 is taken as the last economically stable year available in our data.
```{r Dataset for 2018}

get_year <- function(df, year){
  df %>%
    select(contains(c('region', year)))
}


Data_2018 <- get_year(wide_data, '2018')

```

# Specifications

For non-dynamic models we use the simplified specification without lags.

## Cross-sectional specifications
```{r Specifications, Cross-sectional models}
# Theil index specification
Theil_2018 <- log(GRP_2018) ~ Div_2018 + log(Import_2018) + Edu_2018 + Pop_2018 + Inv_2018 + FDI_2018

# WM and IM specification
Margins_2018 <- log(GRP_2018) ~ EM_2018 + IM_2018 + log(Import_2018) + Edu_2018 + Pop_2018 + Inv_2018 + FDI_2018
```

## Panel specifications
```{r Specifications, Panel models}
# Theil index specification
Theil <- log(GRP) ~ Div + log(Import) + Edu + Pop + Inv + FDI 

# EM and IM specification
Margins <- log(GRP) ~ EM + IM + log(Import) + Edu + Pop + Inv + FDI
```

# Cross-sectional models

```{r Cross-sectional models, echo = TRUE, warning = FALSE}
# Theil index specification
reg_Theil_2018 <- lm(Theil_2018, data = Data_2018)

vcov2_Theil_2018 <- vcovHC(reg_Theil_2018, type = "HC0")
se2imp_Theil_2018 <- sqrt(diag(vcov2_Theil_2018))

# WM and IM specification
reg_Margins_2018 <- lm(Margins_2018, data = Data_2018)

vcov2_Margins_2018 <- vcovHC(reg_Margins_2018, type = "HC0")
se2imp_Margins_2018 <- sqrt(diag(vcov2_Margins_2018))

# Table
stargazer(reg_Theil_2018, reg_Margins_2018, se = list(se2imp_Theil_2018, se2imp_Margins_2018), type = 'text', omit = c('Constant'), keep.stat = c("n")) # font.size = "tiny"
```
# Panel models

Fix negative values (problems with covariance matrix).

```{r Fix negative values}

# data_long_positive <- long_data                    # Duplicate data frame
# data_long_positive[data_long_positive < 0] <- 0     # Set negative values to 0
# data_long_positive

```


### Theil specification
Pooled OLS Theil
```{r Pooled OLS Theil}

ols_plm_Theil <- plm(Theil, 
               data = long_data, 
               index = c("region", "year"),
               model = "pooling")
cov_ols_plm_Theil <- vcovHC(ols_plm_Theil, type = "HC3")
se_ols_plm_Theil <- sqrt(diag(cov_ols_plm_Theil))
coeftest(ols_plm_Theil, df = Inf, vcov = cov_ols_plm_Theil)

```
Fixed (individual) effects Theil
```{r Fixed (individual) effects Theil}
fe_ind_Theil <- plm(Theil, 
              data = long_data, 
              index = c("region", "year"),
              effect = "individual",
              model = "within")
# model.matrix(log(GRP) ~ Import, data = long_data)
cov_fe_ind_Theil <- vcovHC(fe_ind_Theil, type = "HC3")
se_fe_ind_Theil <- sqrt(diag(cov_fe_ind_Theil))
# coeftest(fe_ind_Theil, df = Inf, vcov = cov_fe_ind_Theil)

```
Random Effects Theil
```{r Random Effects Theil}
re_Theil <- plm(Theil, 
              data = long_data, 
              index = c("region", "year"),
              model = "random")
cov_re_Theil <- vcovHC(re_Theil, type = "HC3")
se_re_Theil <- sqrt(diag(cov_re_Theil))
#coeftest(re_Theil, df = Inf, vcov = cov_re_Theil)

```

Panel regressions table, Theil
```{r Panel regressions table, echo = TRUE, warning = FALSE}
stargazer(ols_plm_Theil, re_Theil, fe_ind_Theil, se = list(se_ols_plm_Theil, se_re_Theil, se_fe_ind_Theil), type = "text", omit = c('Constant'), keep.stat = c("n")) # font.size = "tiny"
#order: Pooled OLS, RE, FE
```

#### Tests for best panel model for the Theil specification

```{r Ftest Theil}
#Ftest - between fixed effects and pooled OLS
#H0 - pooled OLS are better than fixed effects (because all individual effects are the same)
#H1 - fixed effects are better than pooled OLS ones
pFtest(fe_ind_Theil, ols_plm_Theil)
#fixed effects are better, as expected
```

```{r plmtest Theil}
#plmtest - between random effects and pooled OLS
#H0 - pooled OLS are better than random effects (because all random effects are the same - on panel effect)
#H1 - random effects are better than pooled OLS ones
plmtest(ols_plm_Theil, type = c('bp'))
#random effects are better
```

```{r phtest Theil}
#phtest - between fixed effects and random effects
#H0 - random effects are better than fixed effects (random coef. are more efficient)
#H1 - fixed effects are better than random effects (fixed coef. are more efficient)
phtest(fe_ind_Theil, re_Theil)
#random effects are then fixed ones - unexpected

#fixed effects are better than random effects
```
So, FE expectedly better than Pooled OLS or RE.
Let's build two-ways variant of it.

#### Best panel model for the Theil specification
```{r Best panel model for the Theil specification}
fe_twoways_Theil <- plm(Theil, 
              data = long_data, 
              index = c("region", "year"),
              effect = "twoways",
              model = "within")
# model.matrix(log(GRP) ~ Import, data = long_data)
cov_fe_twoways_Theil <- vcovHC(fe_twoways_Theil, type = "HC3")
se_fe_twoways_Theil <- sqrt(diag(cov_fe_twoways_Theil))
# coeftest(fe_twoways_Theil, df = Inf, vcov = cov_fe_twoways_Theil)

```

### Margins specification
Pooled OLS Margins
```{r Pooled OLS Margins}

ols_plm_Margins <- plm(Margins, 
               data = long_data, 
               index = c("region", "year"),
               model = "pooling")
cov_ols_plm_Margins <- vcovHC(ols_plm_Margins, type = "HC3")
se_ols_plm_Margins <- sqrt(diag(cov_ols_plm_Margins))
coeftest(ols_plm_Margins, df = Inf, vcov = cov_ols_plm_Margins)

```
Fixed (individual) effects Margins
```{r Fixed (individual) effects Margins}
fe_ind_Margins <- plm(Margins, 
              data = long_data, 
              index = c("region", "year"),
              effect = "individual",
              model = "within")
# model.matrix(log(GRP) ~ Import, data = long_data)
cov_fe_ind_Margins <- vcovHC(fe_ind_Margins, type = "HC3")
se_fe_ind_Margins <- sqrt(diag(cov_fe_ind_Margins))
# coeftest(fe_ind_Margins, df = Inf, vcov = cov_fe_ind_Margins)

```
Random Effects Margins
```{r Random Effects Margins}
re_Margins <- plm(Margins, 
              data = long_data, 
              index = c("region", "year"),
              model = "random")
cov_re_Margins <- vcovHC(re_Margins, type = "HC3")
se_re_Margins <- sqrt(diag(cov_re_Margins))
#coeftest(re_Margins, df = Inf, vcov = cov_re_Margins)

```

Panel regressions table, Margins
```{r Panel regressions table, echo = TRUE, warning = FALSE}
stargazer(ols_plm_Margins,  re_Margins, fe_ind_Margins, se = list(se_ols_plm_Margins,se_re_Margins, se_fe_ind_Margins), type = "text", omit = c('Constant'), keep.stat = c("n")) # font.size = "tiny"
#order: Pooled OLS, RE, FE
```

#### Tests for best panel model for the Margins specification

```{r Ftest Margins}
#Ftest - between fixed effects and pooled OLS
#H0 - pooled OLS are better than fixed effects (because all individual effects are the same)
#H1 - fixed effects are better than pooled OLS ones
pFtest(fe_ind_Margins, ols_plm_Margins)
#fixed effects are better, as expected
```

```{r plmtest Margins}
#plmtest - between random effects and pooled OLS
#H0 - pooled OLS are better than random effects (because all random effects are the same - on panel effect)
#H1 - random effects are better than pooled OLS ones
plmtest(ols_plm_Margins, type = c('bp'))
#random effects are better
```

```{r phtest Margins}
#phtest - between fixed effects and random effects
#H0 - random effects are better than fixed effects (random coef. are more efficient)
#H1 - fixed effects are better than random effects (fixed coef. are more efficient)
phtest(fe_ind_Margins, re_Margins)
#random effects are then fixed ones - unexpected

#fixed effects are better than random effects
```
So, FE expectedly better than Pooled OLS or RE.
Let's build two-ways variant of it.

#### Best panel model for the Margins specification
```{r Best panel model for the Margins specification}
fe_twoways_Margins <- plm(Margins, 
              data = long_data, 
              index = c("region", "year"),
              effect = "twoways",
              model = "within")
# model.matrix(log(GRP) ~ Import, data = long_data)
cov_fe_twoways_Margins <- vcovHC(fe_twoways_Margins, type = "HC3")
se_fe_twoways_Margins <- sqrt(diag(cov_fe_twoways_Margins))
# coeftest(fe_twoways_Margins, df = Inf, vcov = cov_fe_twoways_Margins)

```

## Panel models, united tables

Fixing Stargazer
```{r Fixing Stargazer}
# #echo = FALSE, warning = FALSE
# ## Quick fix for stargazer <= 5.2.3 is.na() issue with long model names in R >= 4.2
# # Unload stargazer if loaded
# detach("package:stargazer",unload=T)
# # Delete it
# remove.packages("stargazer")
# # Download the source
# download.file("https://cran.r-project.org/src/contrib/stargazer_5.2.3.tar.gz", destfile = "stargazer_5.2.3.tar.gz")
# # Unpack
# untar("stargazer_5.2.3.tar.gz")
# # Read the sourcefile with .inside.bracket fun
# stargazer_src <- readLines("stargazer/R/stargazer-internal.R")
# # Move the length check 5 lines up so it precedes is.na(.)
# stargazer_src[1990] <- stargazer_src[1995]
# stargazer_src[1995] <- ""
# # Save back
# writeLines(stargazer_src, con="stargazer/R/stargazer-internal.R")
# # Compile and install the patched package
# install.packages("stargazer", repos = NULL, type="source")
```

### All models
```{r All models, echo = TRUE, warning = FALSE}
stargazer(ols_plm_Theil, re_Theil, fe_ind_Theil, # Theil
          ols_plm_Margins, re_Margins, fe_ind_Margins, # Margins
          se = list(
            se_ols_plm_Theil, se_re_Theil, se_fe_ind_Theil, # Theil
            se_ols_plm_Margins, se_re_Margins, se_fe_ind_Margins), # Margins
          type = "text", omit = c('Constant'), keep.stat = c("n"), font.size = "tiny")

# Order: Pooled OLS, RE, FE
```

### The best one, two-ways modifications

```{r The best ones, two-ways modifications, echo = TRUE, warning = FALSE}

stargazer(fe_twoways_Theil, # Theil
          fe_twoways_Margins,# Margins
          se = list(
            se_fe_twoways_Theil,# Theil
            se_fe_twoways_Margins),# Margins
          type = "text", omit = c('Constant'), keep.stat = c("n"), font.size = "tiny")

```

